# Project Progress
## 1. Installing and Loading of Packages
```{r}
if(!require("data.table")){
	install.packages("data.table")
}

if(!require("reshape2")){
	install.packages("reshape2")
}

require("data.table")
require("reshape2")
```

## 2. Load Activity Labels, Features & Extract the Mean and Standard Deviation
```{r}
activity_labels <- read.table("./UCI HAR Dataset/activity_labels.txt")[,2]

features <- read.table("./UCI HAR Dataset/features.txt")[,2]

extract_features <- grepl("mean|std", features)
```

## 3. Load & Proccess the Test Data
```{r}
X_test <- read.table("./UCI HAR DATASET/test/X_test.txt")
y_test <- read.table("./UCI HAR DATASET/test/y_test.txt")
subject_test <- read.table("./UCI HAR DATASET/test/subject_test.txt")

names(X_test) = features
```

## 4. Load Test Activity Labels & Column Bind the Data
```{r}
y_test[, 2] = activity_labels[y_test[, 1]]
names(y_test) = c("Activity_ID", "Activity_Label")
names(subject_test) = "subject"


test_data <- cbind(as.data.table(subject_test), y_test, X_test)
```

## 5. Load & Proccess Train Data, & Extract Mean & Std Measurements
```{r}
X_train <- read.table("./UCI HAR Dataset/train/X_train.txt")
y_train <- read.table("./UCI HAR Dataset/train/y_train.txt")

subject_train <- read.table("./UCI HAR Dataset/train/subject_train.txt")

names(X_train) = features

X_train = X_train[, extract_features]
```

## 6. Load Train Activity Labels & Column Bind the Data
```{r}
y_train[,2] = activity_labels[y_train[,1]]
names(y_train) = c("Activity_ID", "Activity_Label")
names(subject_train) = "subject"

train_data <- cbind(as.data.table(subject_train), y_train, X_train)
```

## 7. Row Bind the Data
```{r}
data = rbind(test_data, train_data)
```

## 8. Merge Test & Train Data
```{r}
id_labels = c("subject", "Activity_ID", "Activity_Label")
data_labels = setdiff(colnames(data), id_labels)
melt_data = melt(data, id = id_labels, measure.vars = data_labels)
```

## 9. Apply Mean Function, and Write the Tidy Data File
```{r}
tidy_data <- dcast(melt_data, subject + Activity_Label ~ variable, mean)

write.table(tidy_data, file = "./tidy_data.txt")
```
